---
title: "Bar Plots For Market Share Change"
author: "Jizhou Kang"
date: "7/31/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=TRUE,fig.width=6,fig.height=4)
```

## Firstly, loading package and data

**Loading Package...**
```{r,message=FALSE,warning=FALSE}
library(dppbar)
```

**Loading Dataset...**

To fully illustrate the usage of package to accomplish this task, we use two datasets of different structure. They are "Chinese Real Estate Industry Companies' Financial Charts(2007-2016)" and "Some Macroeconomic Data of China(2008-2016)". Head lines of each dataset is shown below.

**Chinese Real Estate Industry Companies' Financial Charts(2007-2016)**
```{r,echo=FALSE}
data("estate_fin_charts")
head(estate_fin_charts[,1:5],5)
```

**Some Macroeconomic Data of China(2008-2016)**
```{r,echo=FALSE}
data("macro_data_chn")
head(macro_data_chn[,1:5],5)
```


## Secondly, done the plot within five lines of R code:

```{r}
bar_plot(dataframe=estate_fin_charts,ctg.idx = 'Year',num.idx = 'income',
         condition.idx = '证券简称',criteria=2016,top_N=10,
         colors=brewer.pal(12,'Set3'),xaxis_name='年份',yaxis_name='营业收入（亿元）',
         title='2016年营业收入前12名房地产企业历年营收变化',
         paper_bgcolor='#ccece6',margin=list(t=36,l=24))
```

```{r}
bar_plot(dataframe=macro_data_chn,ctg.idx='year',num.idx=c(9:12),
         criteria = 2016,colors = brewer.pal(4,'Set1'),
         xaxis_name = '年份',yaxis_name = '商品价格（元/吨）',
         title='一些大宗商品的历年价格变化',
         paper_bgcolor='#ccece6',margin=list(t=36,l=24))
```



**TO:** [Blogs](https://jkang37.github.io/Data-Processing-and-Plotting/Blogs.html)



